%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Article Notes
% LaTeX Template
% Version 1.0 (1/10/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Vel (vel@latextemplates.com)
% Christopher Eliot (christopher.eliot@hofstra.edu)
% Anthony Dardis (anthony.dardis@hofstra.edu)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
10pt, % Default font size is 10pt, can alternatively be 11pt or 12pt
a4paper, % Alternatively letterpaper for US letter
twocolumn, % Alternatively onecolumn
landscape % Alternatively portrait
]{article}

\input{structure.tex} % Input the file specifying the document layout and structure
\usepackage{hyperref}


%----------------------------------------------------------------------------------------
%	ARTICLE INFORMATION
%----------------------------------------------------------------------------------------

\articletitle{Note on Ch.1 Introduction of  \textit{Fixing Language: An Essay for Conceptual Engineering}} % The title of the article
\articlecitation{\cite{Cappelen2018FixingLanguage}} % The BibTeX citation key from your bibliography

\datenotesstarted{November 30, 2018} % The date when these notes were first made
\docdate{\datenotesstarted; rev. \today} % The date when the notes were lasted updated (automatically the current date)
\docauthor{Summarized ands commented by Shimpei Endo} % Your name

%----------------------------------------------------------------------------------------

\begin{document}

\pagestyle{myheadings} % Use custom headers
\markright{\doctitle} % Place the article information into the header

%----------------------------------------------------------------------------------------
%	PRINT ARTICLE INFORMATION
%----------------------------------------------------------------------------------------

\thispagestyle{plain} % Plain formatting on the first page

\printtitle % Print the title

%----------------------------------------------------------------------------------------
%	ARTICLE NOTES
%----------------------------------------------------------------------------------------

\section*{In a nutshell... }


\paragraph{Keywords:}
conceptual engineering,
representational devices,
metasemantics,
Austerity Framework,
representational skepticism,
externalism,
continuity of inquiry

%------------------------------------------------
\section*{1.1 Introduction}
\paragraph{Representational devices=concepts!}
This book is about the process of assesing and improving our \emph{representational devices}, which Capellen calls \emph{concepts}.

\paragraph{A note on the very terminology of \emph{conceptual engineering}. }
After provided the list of similar practices, interestingly (and disapointly for some?), Cappelen confesses:
``It's important that readers don't take that name as a description: on the view I defend in this book, the project isn't about concepts and there isn't really any engeneering.'' (p.4)

\paragraph{The construction of this book}
This book has five parts. Cappelen's positive theory named the Austerity Framework is presented in the middle parts: II thought IV.

\begin{description}
\item[Part I.] Settle down the targets.
Chapter 2 offers examples. Chpater 3 discusses more general issues.
\item[Part II.] Build a metasemantic ground for conceptual engeneering.
Chapter 6 XXX
\item[Part III.] Argue the limit of engeneering.
In particular, Cappelen tackles objections sayning that what he calls conceptual engeneering is just changing the subject.
The objections are constructed in chapter 9 and the following chapters (10 and 11) response to it.
\item[Part IV.] Complete Austery Framework.
\item[Part V.] Consider and compare other approaches.
This part, for instance, considers metasematnic negotiation, conceptual function, and Chalmers' elimination.
\end{description}


\section*{1.2 A Heuristic: representational complacency vs. representational skepticism}

People from different backgrounds other than philosophy can join conceptual engeneering. Cappelen adopts a heuristic for dividing (roughly) people in two groups: the representationally \emph{complacent} and the representationallly \emph{skeptics}.
The complacent does not question concepts given to them.
Note that skeptics on object-level is possible to excute in complacent in meta-level.
The skeptics question concepts given to them and tries to improve them. The latter position is what conceptual engineers should belong to.

\paragraph{Look at himself.}
Cappelen himself is a sample of this tribe.
In fact, Cappelen has argued that concepts such as intuition and de se are so defective as terminologies that cause philosophical problems.
Cappelen mentions that skeptic attitude may also hold to what terminology/concept describes representationally skeptics themselves. An infinite regress? Or we should not talk about them at all because we cannot have a proper language to talka about? Cappelen does not have a conclusive discussion or promissing strategy. Cappelen has rather sees this book as a progress report. As the chapter 2 does, Cappelen has initiated improving projects by showcasing local examples.

\section*{1.3 Central themes of this book}
We will observe several examples in the next chapter 2. Notice that this book does not provide a detailed plan for improvement, which is out of the aim and scope of this monograph. Cappelen sees things more ``from above''.
To avoid losing track, Cappelen lists the six main themes of this book at the end of this introductiory chapter.

\begin{enumerate}
  \item \emph{At the foundation of a theory of conceptual engeneering is a theory of metasemantics!}
See part II. We have not reached any concensus of which metasemantic should be picked.
  \item \emph{Conceptual engeneering is compatible with externalism.}
  A reasonable but unacceptable question towrads conceptual engineers is how to keep consistency with externalism. Given we the users themselves change our concepts used, does not it entail internalism, concepts are all about our mental activities and it is us which determines concepts?
Part II, particularly chapter 6 defends externalims within the Austery Framework.

  \item \emph{In or out of our control?}
  Relating the theme 2, Cappelen takes quite an unique position saying ``not in our control.''
In a nutshell, ``being in control is overrated and for the most part an illusion anyway'' (p.8).

  \item \emph{No systematic theory -- contestation XXX?}

  Warning: this book is not a checklist for successful conceptual engeneering nor a beginner's guide for this engeneering. Instead, this book argues there is no such a thing.
Revisionism works on meta-levels too; the rules governing conceptual engeneering also get improved and revised as concepts in object-level do.

  \item \emph{Conceptual engeneering and continuity of inquiry.}
  See Part III.
Another possible concern is about continuity: can we still keep doing what we have done like arguing, (dis)agreeing on the same thing etc.?
Chapter 9, for example, re-constructs Strawson's worry, which belongs to this line, towrads Carnapian explication. And proceeding chapters will successfully respond it!

  \item \emph{Conceptual engeneering changes the world.}
  For example, when we improve our concept/word `race', we also improve or change race.
Conceptual amelioration (cf. Haslanger) is amelioration of the world.

\end{enumerate}

\section*{Comments by me.}
%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\renewcommand{\refname}{Reference} % Change the default bibliography title

\bibliography{Mendeley} % Input your bibliography file

%----------------------------------------------------------------------------------------

\end{document}
