%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Article Notes
% LaTeX Template
% Version 1.0 (1/10/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Vel (vel@latextemplates.com)
% Christopher Eliot (christopher.eliot@hofstra.edu)
% Anthony Dardis (anthony.dardis@hofstra.edu)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
10pt, % Default font size is 10pt, can alternatively be 11pt or 12pt
a4paper, % Alternatively letterpaper for US letter
twocolumn, % Alternatively onecolumn
landscape % Alternatively portrait
]{article}

\input{structure.tex} % Input the file specifying the document layout and structure
\usepackage{hyperref}


%----------------------------------------------------------------------------------------
%	ARTICLE INFORMATION
%----------------------------------------------------------------------------------------

\articletitle{Summary of ch.18 Conceptual Engineering without Bedrock and without Fixed Points} % The title of the article
\articlecitation{\cite{Cappelen2018FixingLanguage}} % The BibTeX citation key from your bibliography

\datenotesstarted{January 13, 2019} % The date when these notes were first made
\docdate{\datenotesstarted; rev. \today} % The date when the notes were lasted updated (automatically the current date)
\docauthor{Summarized and Commented by Shimpei Endo} % Your name

%----------------------------------------------------------------------------------------

\begin{document}

\pagestyle{myheadings} % Use custom headers
\markright{\doctitle} % Place the article information into the header

%----------------------------------------------------------------------------------------
%	PRINT ARTICLE INFORMATION
%----------------------------------------------------------------------------------------

\thispagestyle{plain} % Plain formatting on the first page

\printtitle % Print the title

%----------------------------------------------------------------------------------------
%	ARTICLE NOTES
%----------------------------------------------------------------------------------------

\section*{In a nutshell... }
This section defends the universal nature of conceptual engineering: anything can be
a target of conceptual engineering.
Cappelen disagrees with Chalmers [18.2] and Eklund [18.3] respectively.

\noindent \textbf{Keywords:} Chalmers, Eklund

\section*{18.1 The Limits of Conceptual Engineering?}
\paragraph{No limit of conceptual engineering. }
Is there any term so fundamental that we cannot conceptual-engineer?
Chalmers and Eklund independenty hold their view supporting that
``there are specific features of specific meanings that make
the idea of evolution problematic'' [p. 194].
Cappelen rejects them.
His recommended hypothesis is: ``\emph{everything is in flux -- that all representational devices
can be revised, and there's no natural end point to conceptual engineering}''[p. 194, his emphasis].

\section*{18.2 Chalmers on Bedrock Concepts}
Chalmers is a supporter of ``bedrock concepts'' \textit{a la} Cappelen, ``expressions that cannot be engineered'' [p. 194].

\paragraph{Chalmers' tenative list of bedrock concepts.}
Chalmers' candidates include: phenomenal concepts, normative concepts, logical or mathematical concepts,
spatiotemporal concepts, indexical concepts, cocepts of explanation; furthermore,
secondary qualities, intentional states, freedom.
\cite[p.552]{Chalmers2011}


\paragraph{Asymmetrical structure among the space of disputes.}
Chalmers observes an asymmetrical structure within the space of disputes. For instance, `ought' is more basic than `murder'.
Chalmers did not give a conclusive argument but believes his idea is ``a promising working hypothesis''.
\cite[p.548-549]{Chalmers2011}

\paragraph{Cappelen does not follow Chalmers.}
[p. 195]
Cappelen suggests another conjecture instead of Chalmers's.
Cappelen criticizes empirical nature of Chalmers' conjecture.
It may capture how disputes end (reaching the bedrock concepts) and how they start (with no bedrock concept).
We need more detailed historical evidence to import empirical guesses to (meta?)philosophical disputes.

\paragraph{Cappelen's conjecture. }
Cappelen suggests: no such a pattern appears in the actual history of philosophy.
Also, Cappelen (again!) points out that the very terminology of Chalmers (e.g. the structure of a debate, bottoming out) must confront debate. In conclusion, we shoul adopt the hypothesis: ``It's conceptual engineering all the way down'' [p. 195].

\section*{18.3 Eklund on Normative Limits}
\paragraph{Eklund: we cannot engineer normative concepts.}
According to Eklund, we cannot revise some normative concepts (e.g. `right' `good' or `ought') being used in the process of conceptual engineering.
``[O]ur thinnest normative concepts are irreplaceable''[p. 197].

\paragraph{Eklund's dilemma.}
``Either there is this further ineffable question or we end up embracing a conclusion that is ``antithetical to the spirit of realism''. Sure. this is wrong, but not wrong*!

\paragraph{Cappelen's responses.}
Cappelen offers three quick and moderate counterarguments towards Eklund.

\begin{enumerate}
  \item Realists do not care the second horn of the dilemma.
  \item Undetective disagreement?
  \item Beyond the semantic values.
\end{enumerate}

\section*{Comments by Endo}
%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

%\renewcommand{\refname}{Reference} % Change the default bibliography title

\bibliography{Mendeley} % Input your bibliography file

%----------------------------------------------------------------------------------------

\end{document}
